---
title: "Comparison of Lloyds & Natwest Financial Accounts"
author: "Dylan Viswambaran"
date: "18/09/2021"
output: 
  html_document:
    toc: true
    toc_float: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r source, echo=FALSE, message=FALSE, warning=FALSE}
source("tidybs.R")

```

## Introduction

In this article we will be exploring the financial results of Lloyds Banking Group and Natwest Group for the Financial Years (FY) 2019 and 2020.

## Income statement

### Total Income

The income statement shows how much revenue a company earned over a specific time period in this case we are going to look at the two groups in question over 2019-2020.

```{r total_income, echo=FALSE}
total_income
```

`r total_income$data$Entity[3]` total income in 2020 was `r paste0("£", comma(total_income$data$Value[4]))` compared to `r paste0("£", comma(total_income$data$Value[3]))` in 2019 which is a **decrease** of `r percent(abs(total_income$data$Value[4] / total_income$data$Value[3] -1))`


`r total_income$data$Entity[1]` total income in 2020 was `r paste0("£", comma(total_income$data$Value[2]))` compared to `r paste0("£", comma(total_income$data$Value[1]))` in 2019 which is a **decrease** of `r percent(abs(total_income$data$Value[2] / total_income$data$Value[1] -1))`


### Impairment losses


Impairment occurs when a business asset suffers a depreciation in fair market value in excess of the book value of the asset on the company's financial statements. The technical definition of impairment loss is a decrease in net carrying value of an asset greater than the future undisclosed cash flow of the same asset.

One of the contributing factors between 2019 and 2020 is a spike in impairment losses as shown in the chart below. 

```{r impairment}

impairment


```


`r impairment$data$Entity[3]` total income in 2020 was `r paste0("£", comma(impairment$data$Value[4]))` compared to `r paste0("£", comma(impairment$data$Value[3]))` in 2019 which is an **increase** of `r percent(impairment$data$Value[3] / impairment$data$Value[4])`


`r impairment$data$Entity[1]` total income in 2020 was `r paste0("£", comma(impairment$data$Value[2]))` compared to `r paste0("£", comma(impairment$data$Value[1]))` in 2019 which is an **increase** of `r percent(impairment$data$Value[1] / impairment$data$Value[2])`

